---
output:
  rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

  library(magrittr)

```

# `envFunc`: an R package of tools to help with other `env`Packages

<!-- badges: start -->
<!-- badges: end -->

The goal of `envFunc` is to store functions that help across the other `env`Packages.

## Installation

`envFunc` is not on [CRAN](https://CRAN.R-project.org).

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Acanthiza/envFunc")
```

Load `envFunc`

```{r}
library("envFunc")
```

## Add time stamp

`add_time_stamp` adds the creation time of an object as an attribute.

```{r}

  temp <- cars %>%
    envFunc::add_time_stamp()

  attr(temp, "ctime")

```

## Add a likelihood classification

```{r}

  x <- tibble::tibble(x = rbeta(10, 1, 1)) %>%
    add_likelihood(x)
  
  x

```

## What else is in `envFunc`

The following functions and data sets are provided in `envFunc`. See https://acanthiza.github.io/envFunc/ for more examples.

```{r, echo = FALSE, warning = FALSE}

  get_name_title <- function(text) {
    
    tibble::enframe(text
                    , name = NULL
                    , value = "description"
                    ) %>%
      dplyr::filter(grepl("title", description)) %>%
      dplyr::mutate(description = gsub("\\\\|title", "", description)
                    , description = gsub("^\\{|\\}$", "", description)
                    )
    
  }

  manuals <- fs::dir_info("man") %>%
    dplyr::select(path) %>%
    dplyr::filter(grepl("Rd$", path)
                  , !grepl("pipe", path)
                  ) %>%
    dplyr::mutate(object = gsub("man\\/|\\.Rd","",path)
                  , class = purrr::map_chr(object, ~envFunc::vec_to_sentence(class(get(.))))
                  , text = purrr::map(path, readLines)
                  , text = purrr::map(text, get_name_title)
                  , object = paste0("`envFunc::"
                                    , object
                                    , "`"
                                    )
                  ) %>%
    tidyr::unnest(cols = c(text))

  knitr::kable(manuals[,2:4])

```




